The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-13 analysis/paper/paper.qmd
Cache text extracted from pdfs
Clean up comments in setup code chunk

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                        # Managing paths
  "tidyverse",                                   # Data manipulation and visualisation
  "tidytext", "SnowballC", "tm", "topicmodels",  # Text processing and analysis
  "tidygeocoder",                                # Working with spatial data
  "igraph", "ggraph"                             # Network analysis and visualsation
)

@@

# library(here)
# library(tidyverse)
# library(tidytext)
# library(SnowballC)
# library(tm)
# library(topicmodels)
# library(tidygeocoder)
# library(igraph)
# library(ggraph)

>>>>

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                        # Managing paths
  "tidyverse",                                   # Data manipulation and visualisation
  "tidytext", "SnowballC", "tm", "topicmodels",  # Text processing and analysis
  "tidygeocoder",                                # Working with spatial data
  "igraph", "ggraph"                             # Network analysis and visualization
)

@@
